A User-Extensible and Adaptable Parser Architecture

### 2008-12-07 doc/sgai-2008-slides.tex
Minor corrections and improvements; XXX items dealt with.

\author{John Tobin \and Carl Vogel}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Trinity College]
{
  School of Computer Science and Statistics\\
  Trinity College, University of Dublin
}

@@

\begin{frame}
    \timingnote{30 seconds}
    \titlepage{}
    XXX EMAIL ADDRESSES\@.
\end{frame}

\begin{frame}{Outline of this talk}
    \timingnote{30 seconds --- 1 minute}
    \tableofcontents{}
\end{frame}

@@

        \item [Currently] Most anti-spam techniques are content-based, and
            require each mail to be accepted before determining its spam
            status.

        \item [However] Rejecting mail at SMTP-time is more efficient, and
            senders of non-spam mails that are incorrectly rejected will be
            informed immediately.

@@

        \item [Method] Parse Postfix log files and analyse the data
            extracted.

        \item [Conclusion] This requires a parser for Postfix log files.

@@

\section{Input characteristics}

\begin{frame}{Input characteristics}

@@

        \item The processing required for a type of log line (e.g.\ a
            remote server connecting to send mail) rarely changes, but it
            can be quite complex.

@@

    XXX SAMPLE LOG LINE\@; MAYBE HOW IT IS PARSED\@?

@@

        \item [Framework] The framework handles loading rules and providing
            support functions to actions, e.g.\ data storage, inter-action
            communication, and utility functions.  For each input log line,
            the framework tries each rule in turn until one matches, then
            it invokes the action specified by the rule.

        \item [Actions] Each action performs the processing required, e.g.\
            XXX GIVE SOME EXAMPLES\@.

@@

        \item Rules can be tagged with conditions which must hold before
            the rule will be used to match an input.  XXX MAYBE EXTEND THIS
            A LITTLE WITH AN EXAMPLE\@?  DO I NEED AN EXAMPLE, WHEN THERE'S
            ONE IN A COUPLE OF SLIDE'S TIME\@?

@@

        \item Most actions are triggered by one or two rules, because they
            deal with special cases.  Three actions are triggered by more
            than 40 rules.  \timingnote{build/stats-action-distribution}
            XXX EXPAND ON THIS\@?

@@

        \item Median throughput when parsing 93 log files is 80.85~MB
            (480,569 log lines) parsed per minute.

        \item Rules are tagged with the name of a Postfix daemon, and will
            only be used to parse log lines produced by that daemon.

@@

        \item Use Machine Learning instead of writing rules; Instance Based
            Learning techniques a requirement due to the size of the data
            set.  \timingnote{Compare to SLCT-based tool.}

        \item Detection of overlapping rules.  XXX MORE DETAILS\@.

        \item XXX REFERENCE IMPLEMENTATION\@?

@@

        \item East to develop a flexible yet strict parser.

>>>>

\author[John Tobin \and Carl Vogel]{John Tobin \and Carl Vogel\\
    tobinjt@cs.tcd.ie vogel@cs.tcd.ie}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Trinity College]
{
    School of Computer Science and Statistics,\\
    Trinity College, University of Dublin
}

@@

\begin{frame}
    \timingnote{30 seconds}
    \titlepage{}
\end{frame}

\begin{frame}{Outline Of This Talk}
    \timingnote{30 seconds --- 1 minute}
    \tableofcontents{}
\end{frame}

@@

        \item [Currently] Most commonly used anti-spam techniques are
            content-based, and require each mail to be accepted before
            determining its spam status.

        \item [However] Rejecting mail at SMTP-time is more efficient, and
            senders of non-spam mails that are incorrectly rejected will
            receive a bounce notification immediately.

@@

        \item [Method] Parse Postfix log files and analyse the
            extracted data.

        \item [Conclusion] This method requires a parser for Postfix log
            files.

@@

\section{Input Characteristics}

\begin{frame}{Input Characteristics}

@@

        \item The processing required for a type of log line (e.g.\
            rejecting a mail delivery attempt) rarely changes, but it can
            be quite complex.

@@

    Sample log line: \texttt{NOQUEUE\@: reject: RCPT from
    client.example.net[192.0.2.1]: 554 5.7.1 <alice@example.net>: Relay
    access denied; from=<eve@example.com> to=<alice@example.net> proto=SMTP
    helo=<client.example.com>}

@@

        \item [Framework] The framework manages rules and provides support
            functions to actions, e.g.\ data storage, inter-action
            communication, and utility functions.  For each input log line,
            the framework tries each rule in turn until one matches, then
            it invokes the action specified by the rule.

        \item [Actions] Each action performs the processing required, e.g.\
            create a new data structure when a client connects; record than
            an anti-spam measure was successful; commit the data structure
            when all processing is complete.

@@

        \item Rules can be tagged with conditions which must hold before
            the rule will be used to match an input.

@@

        \item Most actions are triggered by only one or two rules.

        \item The top three actions are triggered by 41, 49, and 59 rules.
            \timingnote{build/stats-action-distribution}
            \timingnote{uninteresting, save\_data, delivery\_rejected}

@@

        \item Median throughput is 80.85~MB (480,569 log lines) parsed per
            minute.

        \item Rules are tagged with the name of a Postfix component, and
            will only be used to parse log lines produced by that
            component.

@@

        \item Use Machine Learning techniques instead of writing rules;
            Instance Based Learning techniques must be used due to the size
            of the data set.  \timingnote{Compare to SLCT-based tool.}

        \item Detection of overlapping rules: intersection of Finite
            Automata or Push-Down Automata.

        \item Provide a reference implementation.

@@

        \item Easy to develop a flexible yet strict parser.
